LogChunks: A Data Set for Build Log Analysis

### 2020-01-31 msr-paper/paper.tex
Enable review mode
Add reference

%%
%% This is file `sample-sigconf.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigconf')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigconf.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf]{acmart}

@@

\author{Carolin E. Brandt, Annibale Panichella, Andy Zaidman, Moritz Beller}
\email{{c.e.brandt,a.panichella,a.e.zaidman,m.m.beller}@tudelft.nl}
\affiliation{
  \institution{Delft University of Technology}
  \country{The Netherlands}
}

@@

We believe that having a common dataset to be able to fairly compare
different build log analysis techniques will advance the research
area. It will ultimately increase our understanding of CI build
failures. In this paper, we present \logchunks, a collection of 797
annotated Travis CI build logs from 80 GitHub repositories in 29
programming languages. For each build log, \logchunks contains a
manually labeled log part (chunk) describing why the build failed. We
externally validated the data set with the developers who caused the
original build failure.

@@

Thus, in this paper, we present \logchunks,\footnote{\logchunks
  is openly available on Zenodo: https://zenodo.org/record/3632351} a
collection of 797 Travis CI build logs from 80 highly popular GitHub repositories in
29 programming languages.  For each build log, we manually labeled
the chunk describing why the build failed.  The data set also provides
keywords the authors would use to search for the labeled log chunk and
categorizes the log chunks according to their format within the log.

@@

\subsection{Log Collection}
In this section, we describe along the overview in
\Cref{fig:lc-overview} how we created \logchunks. All steps are
automatized as Ruby scripts\footnote{Data collection scripts avaliable
  on GitHub: http://tiny.cc/data-collection} and highly configurable.

@@

\paragraph{Results}
In total, from 2020-10-15 to 2020-10-17, we sent out mails to 246 developers. 32 of these mails could
not be delivered. We performed the sending out in three batches and used the first author's academic email address as the sender. All emails were specific to each recipient, and we only sent one mail per recipient. We received answers from 61 developers, corresponding to
144 build logs (response rate: 24.8\%). When comparing this response rate with other typical response rates known from Software Engineering, it is extremely high. We believe that our personalization and the ease of use for the responder are the main reasons for this---simply clicking on a link to confirm or refute an answer is enough, there is no need to craft an answer. Indeed, we only received seven replies from developers along the lines of ``done''.

@@

% \subsection{Travis CI Build Log Data Set}
% \todo{I would remove this as it is not really related because it does not contain labels?}
% Loriot et al.~\cite{loriot2019dataset, loriot2019styler} collected Travis CI build logs from 130 GitHub repositories to analyze their use of the Checkstyle plugin.
% They selected Maven repositories that included the Checkstyle plugin.
% Their data set only provides the plain build logs, whereas \logchunks additionally provides manually labeled data about the chunk describing why a build failed.

>>>>

%%
%% This is file `sample-sigconf.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigconf')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigconf.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf,review]{acmart}

@@

\author{Carolin E. Brandt, Annibale Panichella, Andy Zaidman, Moritz Beller}
\email{{c.e.brandt, a.panichella, a.e.zaidman, m.m.beller}@tudelft.nl}
\affiliation{
  \institution{Delft University of Technology}
  \country{The Netherlands}
}

@@

We believe that having a common data set to be able to fairly compare
different build log analysis techniques will advance the research
area. It will ultimately increase our understanding of CI build
failures. In this paper, we present \logchunks, a collection of 797
annotated Travis CI build logs from 80 GitHub repositories in 29
programming languages. For each build log, \logchunks contains a
manually labeled log part (chunk) describing why the build failed. We
externally validated the data set with the developers who caused the
original build failure.

@@

Thus, in this paper, we present
\logchunks~\cite{brandt_carolin_2020_3632351},\footnote{\logchunks is
  openly available on Zenodo: https://zenodo.org/record/3632351} a
collection of 797 labeled Travis CI build logs from 80 highly popular GitHub
repositories in 29 programming languages with  we
manually labeled the chunk describing why the build failed.  The data
set also provides keywords the authors would use to search for the
labeled log chunk and categorizes the log chunks according to their
format within the log.

@@

\subsection{Log Collection}
In this section, we describe along the overview in
\Cref{fig:lc-overview} how we created \logchunks. All steps are
automatized as Ruby scripts\footnote{Data collection scripts and their original parametrization are included in the data set.} and highly configurable.

@@

\paragraph{Results}
In total, from 2020-10-15 to 2020-10-17, we sent out mails to 246 developers. 32 of these mails could
not be delivered. We performed the sending out in three batches and used the first author's academic email address as the sender. All emails were specific to each recipient, and we only sent one mail per recipient. We received answers from 61 developers, corresponding to
144 build logs (response rate: 24.8\%). Compared to typical response rates known from Software Engineering~\cite{smith2013improving}, this is very high. We believe that our personalization and the ease of use for the responder are the main reasons for this---simply clicking on a link to confirm or refute an answer is enough, there is no need to craft an answer. Indeed, we only received seven replies from developers along the lines of ``done''.

@@

% \subsection{Travis CI Build Log Data Set}
% \todo{I would remove this as it is not really related because it does not contain labels?}
% Loriot et al.~\cite{loriot2019data set, loriot2019styler} collected Travis CI build logs from 130 GitHub repositories to analyze their use of the Checkstyle plugin.
% They selected Maven repositories that included the Checkstyle plugin.
% Their data set only provides the plain build logs, whereas \logchunks additionally provides manually labeled data about the chunk describing why a build failed.
